Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 paper/paper.tex
Paper seems good

\usepackage[autosize]{dot2texi}
\usepackage[dvipsnames]{xcolor}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{listings}

@@

Media companies produce ever larger numbers of articles, videos, podcasts,
games, etc. -- commonly collectively known as ``content''. A successful
content-producing website not only has to develop systems to aid producing and
publishing that content, but there are also demands to engineer effective
mechanisms to aid consumers in finding that content.

Approaches to aid discovery of content used in industry include providing a
text-based search, hierarchical
categorisation (and thus navigation thereof) and even more tailored recommended
content based on past behaviour or content enjoyed by friends (or sometimes
simply other consumers who share your preferences).

@@

\subsection{Data Pipeline}

The overall content miner system conflates the two jobs of generating
feature sets suitable for data mining and also the data mining process itself.
Thus a core subsystem in the overall system is a conceptual data pipeline whose
input is a URI or IRI identifying a content item published on an organisation's
website and the output is feature sets ready for applying machine learning.

This subsystem was conceptually modelled as a data ``pipeline'' that takes
an IRI identifying a piece of web content at the source end and produces
feature sets at the other end. In this pipeline, the three primary data
structures employed are the \emph{IRI}\footnote{http://tools.ietf.org/html/rfc3987}
(in many cases the public URL for the content's primary page is sufficient),
the \emph{feature set} (modelled as a schema-less set of key-value pairs)
and the \emph{RDF graph} as an intermediate structure for manipulating along
the pipeline.

@@

Note that this ignores triples whose objects are literals, for which case the
a analogous strategy as shown in listings~\ref{literal-sparql} was employed to
produce features of the form: \texttt{?p=?v}.

@@

With the knowledge only of a content item's IRI, we are arguably only able to
produce an empty named RDF graph. Such a graph for an example IRI
\texttt{http://example.com/entity/} is illustrated in
JSON-LD syntax in Listings~\ref{lst:jsonld-identity}. This provides our
base case in the inductive design. This enables a \emph{null} pipeline
as shown in Figure~\ref{fig:gen-null}.

@@

@@

@@

@@

\section{Evaluation}

@@

>>>>

\usepackage[autosize]{dot2texi}
\usepackage[dvipsnames]{xcolor}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{listings}
\usepackage{tikz}
\usepackage{rotating}

@@

Media companies produce ever larger numbers of articles, videos, podcasts,
games, etc. -- commonly collectively known as ``content''. A successful
content-producing website not only has to develop systems to aid producing and
publishing that content, but there are also demands to engineer effective
mechanisms to aid consumers in finding that content. Examples include providing a
text-based search, hierarchical
categorisation and tailored recommended
content based on past behaviour.

@@

\subsection{Data Pipeline}
\label{sec:design-pipeline}

This input side of the miner was conceptually modelled as a data ``pipeline'' that takes
an IRI identifying a piece of web content at the source end and produces
feature sets at the other end. In this pipeline, the three primary data
structures employed are the \emph{IRI}\footnote{http://tools.ietf.org/html/rfc3987}
(in many cases the public URL for the content's primary page is sufficient),
the \emph{feature set} (modelled as a schema-less set of key-value pairs)
and the \emph{RDF graph} as an intermediate structure for manipulating along
the pipeline.

@@

Note that this ignores triples whose objects are literals, for which case the
similar strategy as shown in listings~\ref{lst:literal-sparql} was employed to
produce features of the form: \texttt{?p=?v}.

@@

With the knowledge only of a content item's IRI, we are arguably only able to
produce an empty named RDF graph. Such a graph for an example IRI
\texttt{http://example.com/entity/} is illustrated in
JSON-LD syntax in Listings~\ref{lst:jsonld-identity}. This provides our
base case in the inductive design. This enables a \emph{null} pipeline
as shown in Figure~\ref{fig:gen-null} that only produce feature sets with
a single property containing the item's IRI.

@@

\begin{figure*}
  \begin{center}
    \begin{dot2tex}[dot,options=-t math,autosize,pgf,scale=0.6]
      digraph g {
        rankdir=LR;

        node [shape=circle,margin="0,0"]
        RDF1 [label="RDF_1"];
        RDF2 [label="RDF_2"];
        RDF3 [label="RDF_3"];
        RDFp [label="RDF'"];
        RDFp1 [label="RDF'_1"];
        RDFp2 [label="RDF'_2"];
        RDFp3 [label="RDF'_3"];
        RDFp4 [label="RDF'_4"];

        IRI -> RDF1 [label="\text{parse}"];
        IRI -> RDF2 [label="\text{extract}"];
        IRI -> RDF3 [label="\text{scrape}"];

        RDF1 -> RDF [label="\cup"];
        RDF2 -> RDF [label="\cup"];
        RDF3 -> RDF [label="\cup"];

        RDF -> RDFp1 [label="\text{dereference/parse}"];
        RDF -> RDFp2 [label="\text{hypernym inference}"];
        RDF -> RDFp3 [label="\text{expert inference}"];
        RDF -> RDFp4 [label="\text{OWL inference}"];

        RDF -> RDFp [label="\cup"];
        RDFp1 -> RDFp [label="\cup"];
        RDFp2 -> RDFp [label="\cup"];
        RDFp3 -> RDFp [label="\cup"];
        RDFp4 -> RDFp [label="\cup"];

        RDFp -> Features [label="\text{content\_?p\_?v}"];
        RDFp -> Features [label="\text{content\_?p1\_?p2\_?v}"];
      }
    \end{dot2tex}
  \end{center}  \caption{\label{fig:maximal-pipeline}Maximal Data Pipeline}
\end{figure*}

@@

This could lead to a theoretical maximum pipeline as depicted in Figure~\ref{fig:maximal-pipeline}.

@@

All functionality was implemented as part of a single Python module
named \emph{distillery}
that is run via the Unix command line, with different subcommands for
each feature. Each command was designed around the
Unix Philosophy\cite{raymond2003art} of doing one job per command and
that they were composable via Unix pipes. This allows pipelines to
be composed, e.g.:

\begin{centering}
  \begin{lstlisting}[
      basicstyle=\scriptsize,
      label=lst:unix-pipe,
      language=bash]
distillery extract <iris.txt | distillery enrich
  \end{lstlisting}
\end{centering}

\noindent that resemble the entire theoretical data pipeline described
in section~\ref{sec:design-pipeline} without the need for middleware
such as message queues. More typical enterprise architectures around
message oriented middleware or event-driven architecture might need
to be employed to scale this system to millions of documents, but
the simple approach above is sufficient for tens of thousands of
documents.

@@

Clusters produced were analysed both by an exploratory analysis of the results
and also a survey given to 30 respondents to evaluate mock-ups of
suggested, "related" content based on a hypothetical starting page and
promoted links to other pages in the same cluster.

Exploratory analysis showed a large variety in the sizes of clusters produced.
Hyperlink relationships fell down on finding links to common pages like FAQs
which then allowed the greedy clustering algorithms to spend too much time
grouping all pages that linked to those very common links.

Embedded semantics did well where annotations were put in place for social
media sharing. There was some difficulties with noise from semantic vocabularies
concerned with describing structure of the page or even schema properties
about the properties themselves.

Entity extraction was strong at finding larger numbers of triples, but required
some monitoring to avoid false positives from words common to many pages
(a large number of BBC pages mention Twitter, for example, where there
are controls prompting users to share content on that platform). Other examples
included a ``Listen'' button present on all BBC pages about radio programmes.

Enrichment by dereference had the same shortcomings of embedded semantics
extraction and whilst it did add value in some cases, it generated an explosive
increase in the number of triples that had a large impact on system performance.

Results from the survey supported the idea that embedded entities pleased
users where it was able to group things on very structural, categorical aspects
of the data (e.g. BBC News vs. BBC iPlayer or even ``Football'' category
within BBC Sport.)

However, many users preferred items to be linked more strongly by theme or
topic. Some useful discussion with user experience experts supported this idea
and in some cases this was achieved due to entity extraction.

@@

Extracting embedded semantics provided enough initial benefits for machine
learning in that a model can be produced that understands the broad categorisation
of media content. That it is far simpler to implement than bespoke enterprise
integration projects, proves its worth as an initial iteration of a more
intelligent system.

Organisations would benefit from implementing this baseline for gaining
insights into its content and then spend later iterations looking at
introducing entity extraction, monitored carefully for appropriate tuning.

Later iterations can look at some enterprise integration work to improve
the quality of the most poorly-performing content items. there is certainly
need for future work to evaluate some of the more complex enrichment approaches.
